Interoception Scale - Data Cleaning

### 2024-12-11 study1/analysis/1_cleaning.qmd
update
@EmmaLBenn @maisiebennett could you remove the paragraph on mahalanobis distance and try to add a few sentences + ref on what we actually did (OPTICS)

@@

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

@@

### Ethinicity

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```
:::

```{r p_summary}

p_map
p_age
p_edu
```

>>>>

We removed `r length(outliers$duration)` (`r insight::format_percent(length(outliers$duration) / nrow(df))`) participants for having completed the experiment in less than 5 minutes.

@@

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12.5, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

@@

### Ethnicity

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```

:::

```{r p_summary}
#| fig-width: 14
#| fig-height: 14

(p_age | p_edu) / p_map
```
